National Longitudinal Study Reveals Growth in Wellbeing Among Those with Spiritual Beliefs

### 2020-11-16 Manuscript.Rmd
fixed "figs" --> "Figs" and testing overleaf push.

```{r fig.cap = "Combination Coefficient Plots for Personal Well-being and Life Satisfaction Spirit Belief Longitudinal Models"}
knitr::include_graphics("figs/USEcoefficientplots-1.png")
```

>>>>

```{r fig.cap = "Combination Coefficient Plots for Personal Well-being and Life Satisfaction Spirit Belief Longitudinal Models"}
knitr::include_graphics("Figs/USEcoefficientplots-1.png")
```
